
```{r}
library(ape)
library(ggdendro)
library(ggplot2)
library(matrixStats)
library(randomcoloR)
library(reshape2)

WORKING.DIR="z:/mchung/lingdi_zhang_01/"
```

## Load upstream data
```{r}
load(paste0(WORKING.DIR,"/virus_upstream.R"))
```

## Calculate relative abundance
```{r}
relab <- as.data.frame(apply(counts,2,function(x){x/sum(x)*100}))
```


## Plot viral MAG counts from each sample

```{r,fig.height=8,fig.width=18}
plot1 <- ggplot()+
  geom_bar(aes(x=colnames(counts),y=colSums(counts)),
           stat="identity")+
  labs(x="",y="viral MAG counts")+
  scale_y_continuous(expand=c(0,NA))+
  theme_bw()+
  theme(axis.text.x = element_blank())

plot2 <- ggplot()+
  geom_bar(aes(x=colnames(counts),y=colSums(counts)),
           stat="identity")+
  labs(x="",y="viral MAG counts")+
  theme_bw()+
  scale_y_continuous(expand=c(0,NA))+
  coord_cartesian(ylim=c(0,100000))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

egg::ggarrange(plot1,plot2,ncol=1)
```

# Plot top viral MAG species hits
```{r,fig.height=7,fig.width=6}
plot.df <- relab[,grep("[Nn]eg",colnames(relab),invert=T)]
top_taxa <- rownames(plot.df)[order(-rowMedians(as.matrix(plot.df)))][1:50]

plot.df <- reshape2::melt(as.matrix(plot.df))
plot.df <- plot.df[plot.df[,1] %in% top_taxa,]
plot.df[,1] <- factor(plot.df[,1],levels=rev(top_taxa))

set.seed(87)
colors <- randomcoloR::distinctColorPalette(k=length(top_taxa))

plot <- ggplot()+
  geom_boxplot(aes(x=plot.df[,3]+1,y=plot.df[,1]),fill=colors)+
  labs(x="",y="",title="Top Viral MAG Species")+
  scale_x_continuous(trans="log10")+
  theme_bw()

plot(plot)


pdf(paste0(WORKING.DIR,"/plots/top_viral_MAG_species.boxplot.pdf"),
    height=7,
    width=6)
plot(plot)
dev.off()
```

## Cluster samples based on taxa profile

```{r,fig.height=8,fig.width=15}
plot.df <- relab[,grep("[Nn]eg",colnames(relab),invert=T)]

dist_mat <- dist(t(plot.df), method = 'euclidean')
hc <- hclust(dist_mat, method = 'ward.D2')
clusters <- cutree(hc,k=4)

hcdata <- as.dendrogram(hc)
hcdata
ggdendrogram(hcdata)+
  theme(axis.text.x=element_text(color=clusters[hc$order]))

phylo <- as.phylo(hc)
plot(as.phylo(hc), type = "unrooted", cex = 0.6,tip.color=clusters,
     no.margin = TRUE)
```

## Plot viral MAG profile for each sample

```{r,fig.height=8,fig.width=18}
plot1.df <- as.data.frame(cbind(names(clusters[hc$order]),
                                colSums(counts[,names(clusters[hc$order])])))
plot1.df[,1] <-factor(plot1.df[,1],levels=plot1.df[,1])

plot1 <- ggplot()+
  geom_bar(aes(x=plot1.df[,1],y=as.numeric(as.character(plot1.df[,2]))),
           stat="identity")+
  labs(x="",y="viral\nMAG counts")+
  theme_bw()+
  scale_y_continuous(expand=c(0,NA))+
  coord_cartesian(ylim=c(0,100000))+
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())

plot2.df <- as.data.frame(cbind(names(clusters[hc$order]),
                                paste0("c",clusters[hc$order])))
plot2.df[,1] <-factor(plot2.df[,1],levels=plot2.df[,1])
plot2 <- ggplot()+
  geom_tile(aes(x=plot2.df[,1],y="Cluster",
                fill=plot2.df[,2]))+
  labs(fill="Cluster")+
  scale_y_discrete(expand=c(0,0))+
  scale_fill_manual(values=c("#000000","#e895b0","#88bf5a","#6ebbf3"))+
  guides(fill=guide_legend(nrow=1))+
  theme_bw()+
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.y = element_blank())


plot3.df <- relab[,names(clusters[hc$order])]
top_taxa <- rownames(plot3.df)[order(-rowMedians(as.matrix(plot3.df)))][1:50]

plot3.df <- reshape2::melt(as.matrix(plot3.df))
plot3.df[,1] <- ifelse(plot3.df[,1] %in% top_taxa,as.character(plot3.df[,1]),"Other")
plot3.df[,1] <- factor(plot3.df[,1],levels=c(top_taxa,"Other"))
plot3.df[,2] <- factor(plot3.df[,2],levels=names(clusters[hc$order]))

plot3 <- ggplot()+
  geom_bar(aes(x=plot3.df[,2],y=plot3.df[,3],fill=plot3.df[,1]),
           stat="identity")+
  labs(x="",y="relative abundance",fill="Taxa")+
  scale_fill_manual(values = c(rev(colors),"darkgrey"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

egg::ggarrange(plot1,plot2,plot3,
               heights=c(1,0.25,10),
               ncol=1)
pdf(paste0(WORKING.DIR,"/plots/viral_MAG_profiles.barplot.pdf"),
    height=8,
    width=20,
    onefile=FALSE)
egg::ggarrange(plot1,plot2,plot3,
               heights=c(1,0.25,10),
               ncol=1)
dev.off()
```


```{r,fig.height=8,fig.width=6}
individuals <- sort(unique(gsub("[.].*","",names(clusters[hc$order]))))

plot.df <- as.data.frame(matrix(nrow=length(individuals),
                                ncol=4))
rownames(plot.df) <- individuals
colnames(plot.df) <- sort(unique(clusters[hc$order]))

for(i in 1:nrow(plot.df)){
  if(rownames(plot.df)[i] != "MG_positive"){
    set <- clusters[grep(paste0(individuals[i],"[.]"),names(clusters))]
  }else{
    set <- clusters[grep(individuals[i],names(clusters))]

  }
  for(j in 1:ncol(plot.df)){
    plot.df[i,j] <- length(which(set == colnames(plot.df[j])))
  }
}
colnames(plot.df) <- paste0("c",colnames(plot.df))

plot.df <- melt(as.matrix(plot.df))
plot.df[,1] <- factor(plot.df[,1],levels=rev(individuals))

ggplot()+
  geom_bar(aes(x=plot.df[,1],y=plot.df[,3],fill=plot.df[,2]),
           stat="identity")+
  scale_fill_manual(values=c("#000000","#e895b0","#88bf5a","#6ebbf3"))+
  labs(x="",y="# of samples",fill="Cluster")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  coord_flip()

```

## Plot cluster profile for each individual

```{r}
plot_braycurtis_mds <- function(counts,groups,title,labs = T){
  counts <- counts[,!(is.na(groups))]
  groups <- groups[!is.na(groups)]
  
  ddsv <- DESeqDataSetFromMatrix(countData = counts,
                                 colData = as.data.frame(groups),
                                 design = ~groups)
  idx <- which(colSums(counts(ddsv)) == 0)
  if(length(idx) > 0){ddsv <- ddsv[ , -idx]}

  gm_mean = function(x, na.rm=TRUE){ exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))}
  geoMeans = apply(counts(ddsv), 1, gm_mean)
  
  ddsv <- estimateSizeFactors(ddsv, geoMeans = geoMeans)
  vsdv <- varianceStabilizingTransformation(ddsv)
  vsdv0 <- ifelse(assay(vsdv)<0,0,assay(vsdv))
  
  vegdist <- vegdist(as.data.frame(t(vsdv0)),method="bray")
  cmdScale <- cmdscale(vegdist, k =10)
  vars <- apply(cmdScale, 2, var)
  percentVar <- round(100 * (vars/sum(vars)))

  newResults <- as.data.frame(cbind(cmdScale,
                                    as.character(vsdv$groups)))
  colnames(newResults)[1] <- "PC1"
  colnames(newResults)[2] <- "PC2"
  colnames(newResults)[ncol(newResults)] <- "groups"
  
  centroids <- aggregate(cbind(as.numeric(as.character(PC1)),
                               as.numeric(as.character(PC2))) ~ groups,
                         data= newResults, mean)
  colnames(centroids) <- c("groups","PC1","PC2")
  newResults <- merge(newResults,centroids,by="groups",suffixes=c("",".centroid"))

  for(i in 2:ncol(newResults)){newResults[,i] <- as.numeric(as.character(newResults[,i]))}
  
  newResults <- as.data.frame(newResults)
  
  data.adonis <- data.frame(colData(vsdv))
        
  samplepermanova <- adonis(vegdist ~ groups, data.adonis)
  samplepermanova <- as.data.frame(samplepermanova$aov.tab)
  samplepermanova <- samplepermanova$'Pr(>F)'[1]
  
  plot.mds <- ggplot() + # Graph PC1 and PC2
    geom_segment(aes(x=!!newResults$PC1.centroid, y=!!newResults$PC2.centroid,
                     xend=!!newResults$PC1, yend=!!newResults$PC2, color=!!newResults$groups))+ 
    geom_point(aes(x=!!newResults$PC1, y=!!newResults$PC2,
                   color=!!newResults$groups),size=5,alpha=0.5) + # Set the size of the points
    #geom_text(aes(x=0.1,y=-0.1),color="black",label=paste0("p<",samplepermanova))+
    labs(title=paste0("Bray-Curtis MDS Plot\n",title," | Pr(>F) = ",samplepermanova),
         x=paste0("MDS1: ",percentVar[1],"% variance"),
         y=paste0("MDS2: ",percentVar[2],"% variance"))+
    guides(color="none")+
    #scale_color_manual(values=c("#1700F5", "#BEBEBE", "#F7A501")) + 
    theme_bw()+
    theme(plot.title = element_text(size=8))
  if(labs == T){
    plot.mds <- plot.mds +
      geom_label_repel(aes(x=!!centroids$PC1, y=!!centroids$PC2, label=!!centroids$groups,color=!!centroids$groups), size=5)
  }
  
  n_samples <- sort(table(groups))[1]
  min_reads <- 10
  taxa <- rownames(counts)[rowSums(counts >= min_reads) >= n_samples]
  wascores <- wascores(cmdScale, as.data.frame(t(vsdv0[taxa,])))
  
  wascores.comp1 <- wascores[order(abs(wascores[,1]),decreasing=T),1][1:20]
  wascores.comp2 <- wascores[order(abs(wascores[,2]),decreasing=T),2][1:20]
    
                     
  plot.wascores.comp1 <- ggplot()+
    geom_bar(aes(x=!!wascores.comp1,
                 y=!!factor(names(wascores.comp1),levels=rev(names(wascores.comp1)))),
             stat="identity")+
    labs(title=paste0("MDS1 WA Scores\n",title),x="weighted average scores",y="")+
    theme_bw()+
    theme(plot.title = element_text(size=8))
  
  plot.wascores.comp2 <- ggplot()+
    geom_bar(aes(x=!!wascores.comp2,
                 y=!!factor(names(wascores.comp2),levels=rev(names(wascores.comp2)))),
             stat="identity")+
    labs(title=paste0("MDS2 WA Scores\n",title),x="weighted average scores",y="")+
    theme_bw()+
    theme(plot.title = element_text(size=8))
  
  plot.list <- list(mds=plot.mds,
                    loadings1=plot.wascores.comp1,
                    loadings2=plot.wascores.comp2)
  return(plot.list)
}
```

```{r,fig.height=6,fig.width=6}
plot.df <- counts[,grep("[Nn]eg",colnames(counts),invert=T)]

title="Viral MAGs"
plot <- plot_braycurtis_mds(plot.df,
                            paste0("c",clusters)
                            ,title,labs = T)
plot$mds+
  scale_color_manual(values=c("#000000","#e895b0","#88bf5a","#6ebbf3"))
```

# DE analysis based off hierarchical clustering groups

## Set DE functions
```{r}
edgeR <- function(counts,groups){
  design <- model.matrix(~groups)

  y <- DGEList(counts=counts,
                 group=groups)
  keep <- filterByExpr(y)  
  y <- y[keep, , keep.lib.sizes = F]
  if(nrow(y$counts) < 10){return(as.data.frame(matrix(nrow=0,ncol=5)))}
  y <- calcNormFactors(y, method="TMM")
  y <- estimateDisp(y,design, robust=TRUE)
  fit <- glmQLFit(y,design,robust=TRUE)
    
  qlf <- glmQLFTest(fit,coef=2:(ncol(design)))
  degenes <- topTags(qlf,n=Inf)
  return(degenes)
}
```

## Run edgeR
```{r}
counts <- counts[,grep("[Nn]eg",colnames(counts),invert=T)]
groups <- paste0("c",clusters)
groups <- factor(groups,levels=c("c1","c2","c3","c4"))

detaxa <- list()
for(i in 1:length(levels(groups))){
  groups.subset <- ifelse(groups == levels(groups)[i],as.character(groups),"other")
  groups.subset <- factor(groups.subset,levels=c(levels(groups)[i],"other"))
  edgeR.output <- edgeR(counts,groups.subset)$table
  detaxa[[i]] <- edgeR.output[order(edgeR.output$FDR),]
}
names(detaxa) <- levels(groups)
```

## Plot distinct taxa for each cluster

```{r,fig.height=7,fig.width=8}
cluster_col <- c("#000000","#e895b0","#88bf5a","#6ebbf3")
plot.df <- as.data.frame(matrix(nrow=0,
                                ncol=4))

plot.list <- list()
for(i in 1:length(detaxa)){
  keytaxa <- detaxa[[i]][detaxa[[i]]$FDR < 0.05 & detaxa[[i]]$logFC < 0,]
  keytaxa <- keytaxa[order(keytaxa$logFC),]
  if(nrow(keytaxa) > 20){
    keytaxa <- keytaxa[1:20,]
  }
  
  plot.df <- as.data.frame(cbind(rownames(keytaxa),
                                 -keytaxa$logFC))
  colnames(plot.df) <- c("taxa","logFC")
  plot.df$relab <- rowMeans(relab[plot.df$taxa,
                                  grep("[Nn]eg",colnames(relab),invert=T)])
  
  plot.df[,1] <- factor(plot.df[,1],levels=rev(plot.df[,1]))
  
  plot.list[[i]] <- ggplot()+
    geom_point(aes(x=!!as.numeric(as.character(plot.df$logFC)),
                   y=!!plot.df$taxa,
                   size=!!plot.df$relab+1),
               alpha=0.75,
               fill=cluster_col[i],
               pch=21)+
    coord_cartesian(xlim=c(-1,5))+
    guides(size="none")+
    labs(x="logFC",y="",size="relab",title=names(detaxa)[i])+
    theme_bw()+
    scale_size(breaks=c(0.01,0.1,1,10),trans="sqrt",limits=c(0.01,40))

}

egg::ggarrange(plots = plot.list,
               nrow=2)

```

## Set WGCNA functions
```{r}
wgcna.plot_soft_power <- function(df){
  powers <- c(c(1:10), seq(from = 12, to=20, by=2))
  sft <- pickSoftThreshold(df, powerVector = powers, verbose = 5)
  text.color <- rep("black",length(sft$fitIndices[,1]))
  scale_independence.plot <- ggplot()+
    geom_text(mapping = aes(x = sft$fitIndices[,1], y = -sign(sft$fitIndices[,3])*sft$fitIndices[,2], label=sft$fitIndices[,1]))+
    labs(title = "scale independence", x = "soft threshold (power)", y = "scale free topology model fit, signed R^2")+
    theme_bw()
  mean_connectivity.plot <- ggplot()+
    geom_text(mapping = aes(x = sft$fitIndices[,1], y = sft$fitIndices[,5], label=sft$fitIndices[,1]))+
    labs(title = "mean connectivity", x = "soft threshold (power)", y = "mean connectivity")+
    theme_bw()
  egg::ggarrange(scale_independence.plot, mean_connectivity.plot,
                 nrow=1,labels = c("A","B"))
}

wgcna.create_TOM_and_modules <- function(df,softpower){
 ### Create adjacency matrix and modules
  adjacency <- adjacency(df, power = softpower)
  TOM <- TOMsimilarity(adjacency)
  rownames(TOM) <- colnames(df)
  colnames(TOM) <- rownames(TOM)
  dissTOM <- 1-TOM
  geneTree <- hclust(as.dist(dissTOM), method = "average");
  minModuleSize <- 1
  dynamicMods <- cutreeDynamic(dendro = geneTree, distM = dissTOM,
                               deepSplit = 2, pamRespectsDendro = FALSE,
                               minClusterSize = minModuleSize)
  dynamicColors = labels2colors(dynamicMods)
  MEList = moduleEigengenes(df, colors = dynamicColors)
  MEs = MEList$eigengenes
  MEDiss = 1-cor(MEs, use = "pairwise.complete.obs")
  METree = hclust(as.dist(MEDiss), method = "average")
  MEDissThres = 0.25

  plot(METree, main = "clustering of module eigengenes",
       xlab = "", sub = "")
  abline(h=MEDissThres, col = "red")
  
  merge = mergeCloseModules(df, dynamicColors, cutHeight = MEDissThres, verbose = 3)
  mergedColors = merge$colors
  mergedMEs = merge$newMEs
  
  plotDendroAndColors(geneTree, cbind(dynamicColors, mergedColors), c("dynamic tree cut", "merged dynamic"),
                      dendroLabels = FALSE, hang = 0.03, addGuide = TRUE, guideHang = 0.05)
  
  module_order <- names(rev(sort(table(mergedColors))))
  modules <- mergedColors
  for(i in 1:length(table(module_order))){
    modules[modules == module_order[i]] <- paste0("m",sprintf("%02d",i))
  }

  wgcna.output <- list(modules = factor(modules,levels=sort(unique(modules))),
                       module_colors = factor(mergedColors,levels=module_order),
                       MEs = mergedMEs,
                       TOM = TOM)
  return(wgcna.output)
}

wgcna.plot_dissTOM_heatmap <- function(wgcna.output,title){
  dissTOM <- 1-wgcna.output$TOM
  geneTree=hclust(as.dist(dissTOM), method="average" )
  
  row_ha.module.col <- names(rev(sort(table((wgcna.output$module_colors)))))
  names(row_ha.module.col) <- names(rev(sort(table((wgcna.output$modules)))))
  
  row_ha <- rowAnnotation(Module=wgcna.output$modules,col=list(Module = row_ha.module.col),show_legend=F)
  column_ha <- columnAnnotation(Module=wgcna.output$modules,col=list(Module = row_ha.module.col))

  heatmap <- Heatmap(dissTOM^4,
                     name = "dissTOM^4",
                     column_title=title,
                     cluster_rows=geneTree,
                     cluster_columns=geneTree,
                     left_annotation = row_ha,
                     top_annotation = column_ha,
                     show_row_names = F,
                     show_column_names = F,
                     col=rev(magma(12)))
  
  return(heatmap)
}


wgcna.plot_gene_network <- function(wgcna.input,wgcna.output,title,dissCutoff){
  dissTOM <- (1 - wgcna.output$TOM)^4
  dissTOM[dissTOM > dissCutoff] = NA
  dissTOM[!is.na(dissTOM)] = 1
  dissTOM[is.na(dissTOM)] = 0
  
  network <- graph.adjacency(dissTOM, mode="undirected")
  V(network)$module <- as.character(wgcna.output$modules)
  V(network)$size <- colMeans(wgcna.input)
  network <- simplify(network)
  network <- igraph::delete.vertices(network, which(igraph::degree(network)==0))
  
  set.seed(84)
  ggnet.wgcna <-fortify(network,layout=layout_nicely(network))
  ggnet.wgcna$module <- factor(ggnet.wgcna$module,levels=sort(unique(wgcna.output$modules)))
  net.plot <- ggplot(ggnet.wgcna, aes(x = x, y = y, xend = xend, yend = yend,color=module,label=name))+
    geom_edges(color="lightgrey",alpha=0.5)+
    geom_nodes(aes(size=size))+
    geom_nodetext(aes(size=size),
                  color="black",alpha=0.7) +
    guides(alpha='none',size='none',color='none')+
    labs(title=title,color="Module")+
    scale_color_manual(values=levels(wgcna.output$module_colors),drop=F)+
    theme_blank()+
    theme(plot.title = element_text(hjust = 0.5),
           legend.position="top")
  
  return(net.plot)
}

wgcna.plot_module_network <- function(wgcna.input,wgcna.output,title,dissCutoff){
  module_color.map <- as.data.frame(cbind(as.character(unique(wgcna.output$modules)),
                                          as.character(unique(wgcna.output$module_colors))))
  colnames(module_color.map) <- c("module","color")
  module_color.map <- module_color.map[order(module_color.map$module),]
  
  MEDiss = (1-cor(wgcna.output$MEs, use = "pairwise.complete.obs"))^4
  MEDiss[MEDiss > dissCutoff] = NA
  MEDiss[!is.na(MEDiss)] = 1
  MEDiss[is.na(MEDiss)] = 0
  rownames(MEDiss) <- module_color.map$module[match(gsub("^ME","",rownames(MEDiss)),module_color.map$color)]
  colnames(MEDiss) <- rownames(MEDiss)
  
  network <- graph.adjacency(MEDiss, mode="undirected")
  V(network)$module <-  as.character(rownames(MEDiss))
  V(network)$size <- table(wgcna.output$modules)[match(V(network)$module,names(table(wgcna.output$modules)))]
  network <- simplify(network)
  network <- igraph::delete.vertices(network, which(igraph::degree(network)==0))
  
  set.seed(84)
  ggnet.wgcna <-fortify(network,layout=layout_nicely(network))
  ggnet.wgcna$module <- factor(ggnet.wgcna$module,levels=sort(unique(wgcna.output$modules)))
  
  net.plot <- ggplot(ggnet.wgcna, aes(x = x, y = y, xend = xend, yend = yend,color=module,label=name))+
    geom_edges(color="lightgrey",alpha=0.5)+
    geom_nodes(aes(size=size))+
    geom_nodetext(color="black") +
    guides(alpha='none',size='none')+
    labs(title=title,color="Module")+
    scale_color_manual(values=levels(wgcna.output$module_colors),drop=F)+
    theme_blank()+
    theme(plot.title = element_text(hjust = 0.5),
           legend.position="top")
  
  net.plot

  return(net.plot)
}

wgcna.module_t_test <- function(wgcna.input,wgcna.output,groups){
  modules <- levels(wgcna.output$modules)
  
  t.test_pvalue <- c()
  for(i in 1:length(modules)){
    t.test_pvalue <- c(t.test_pvalue,
                       t.test(colMeans(wgcna.input[groups == levels(groups)[1],wgcna.output$modules == modules[i]]),
                              colMeans(wgcna.input[groups == levels(groups)[2],wgcna.output$modules == modules[i]]))$p.value)
  }
  plot.df <- unique(as.data.frame(cbind(as.character(wgcna.output$modules),
                                        as.character(wgcna.output$module_colors))))
  colnames(plot.df) <- c("module","colors")
  plot.df <- plot.df[order(plot.df$module),]
  plot.df$pvalue <- t.test_pvalue
  plot.df$fdr <- p.adjust(plot.df$pvalue,method="fdr")
  
  plot.df <- plot.df[plot.df$fdr < 0.05,]
  
  plot.df$module <- factor(plot.df$module,levels=rev(plot.df$module))
  
  plot1 <- ggplot()+
    geom_point(aes(x="t-test FDR",
                   y=!!plot.df$module,
                   size=!!-log10(plot.df$fdr)),
               pch=21,
               fill=plot.df$colors,
               color=ifelse(plot.df$fdr < 0.05,
                             "red","black"),
               alpha=ifelse(plot.df$fdr < 0.05,
                            1,0.5))+
    labs(size="-log10 FDR")+
    theme_bw()+
    theme(axis.text.x = element_text(angle=90,hjust=1,vjust=0.5),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          legend.position = "top")
  
  melt.df <- melt(as.matrix(scale(log2(wgcna.input+1))))
  
  melt.df <- melt(as.matrix(wgcna.input))
  colnames(melt.df) <- c("sample","taxa","relab")
  melt.df$group <- groups[match(melt.df$sample,rownames(wgcna.input))]
  melt.df$module <- wgcna.output$modules[match(melt.df$taxa,colnames(wgcna.input))]
  melt.df <- melt.df[melt.df$module %in% plot.df$module,]
  
  plot2 <- ggplot(data=melt.df,aes(x=group,y=relab+1,fill=group))+
    geom_boxplot()+
    labs(y="log10 relab")+
    facet_wrap(~module, scales="free")+
    #scale_y_continuous(trans="log10")+
    theme_bw()
  
  
  plot.list <- list(dotplot=plot1,
                    boxplot=plot2)
  return(plot.list)
}
```

## Run WGCNA

```{r}
df <- relab[detaxa,grep("[Nn]eg",colnames(relab),invert=T)]
df <- df[rowSums(df) != 0,]
title <- "Virus"

wgcna.input <- as.data.frame(t(df))
# groups <- gsub("_.*","",rownames(wgcna.input))
# groups <- factor(groups,levels=c("COPD","SmNV"))

wgcna.plot_soft_power(wgcna.input)
softpower <- 6

wgcna.output <- wgcna.create_TOM_and_modules(wgcna.input,softpower)
```

### Plot module heatmap

```{r,fig.height=15,fig.width=8}
heatmap.df <- t(scale(t(log2(df+1))))
  
row_order <- rownames(heatmap.df)[order(wgcna.output$modules)]
#col_order <- colnames(heatmap.df)[order(clusters)]
heatmap.df <- heatmap.df[row_order,]

Module.col <- names(table(wgcna.output$module_colors))
names(Module.col) <- sort(unique(wgcna.output$modules))
Clusters.col <- c("c1"="#000000","c2"="#e895b0","c3"="#88bf5a","c4"="#6ebbf3")

row_ha <- rowAnnotation(Module=wgcna.output$modules[order(wgcna.output$modules)],
                        col=list(Module=Module.col))
column_ha <- columnAnnotation(Clusters=paste0("c",clusters),
                              col=list(Clusters = Clusters.col))
col_fun = circlize::colorRamp2(c(-3, 0, 3), c("blue", "white", "red"))

set.seed(96)
Heatmap(heatmap.df,
        name="zscore log2TPM",
        left_annotation=row_ha,
        top_annotation=column_ha,
        use_raster=F,
        cluster_rows=F, 
        cluster_columns=hc,
        show_row_names=F,
        col = col_fun,
        column_names_gp=grid::gpar(fontsize=6))
```

```{r}
dissTOM_heatmap.list[[title]] <- wgcna.plot_dissTOM_heatmap(wgcna.output,title)
gene_network.list[[title]] <- wgcna.plot_gene_network(wgcna.input,wgcna.output,title,dissCutoff=0.6)
module_network.list[[title]] <- wgcna.plot_module_network(wgcna.input,wgcna.output,title,dissCutoff=0.2)
t_test_dotplot.list[[title]] <- wgcna.module_t_test(wgcna.input,wgcna.output,groups)[[1]]
t_test_boxplot.list[[title]] <- wgcna.module_t_test(wgcna.input,wgcna.output,groups)[[2]]

```


```{r,fig.height=11,fig.width=11}
wgcna.plot_gene_network(wgcna.input,wgcna.output,"",dissCutoff=0.6)
```